Stochastic Wind Power Forecasting

### 2020-02-11 LaTeX_code/paper/paper_1line.tex
Added plots in slides and paper, corrected beta function in code

\begin{figure}[h!]
\centering
\includegraphics[width=0.6\textwidth]{plots/initial_guess/initial_theta_1.eps}
\caption{Value function from ($\ref{inital_theta}$) as a function of different $\theta_0$ values. We can observe that the function if flat for a wide range.}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{plots/initial_guess/initial_theta_1.eps}\quad\includegraphics[width=0.42\textwidth]{plots/initial_guess/initial_theta_2.eps}
\caption{Value function from ($\ref{inital_theta}$) as a function of different $\theta_0$ values. We can observe that the function if flat for a wide range.}
\end{figure}

\subsection{Negative Log-Lihelihood}

We plot the Negative Log-Likelihood as a function of the parameters. The plots can be seen in Figure (\ref{fig:neg-LL}). We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.

\begin{figure}[h!]
\centering
\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood.eps}\quad\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_refined.eps}
\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_more_refined.eps}
\caption{Negative Log-Likelihood for different domains.}
\label{fig:neg-LL}
\end{figure}
